---
name: Samuel
surname: Beauregard-Tousignant
position: "M. Sc"
pronouns: he/him
address: "Montreal"
phone: 819-968-9459
#www: mariecurie.com
email: "samuel.beauregard.t@gmail.com"
#twitter: mariecurie
github: SamuelBeauregard
linkedin: Samuel beauregard-tousignant
#date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * I'm passionate about microorganisms and the subsurface 
 * I have specialized myself in HGAM, and really like uncovering patterns in big data sets using statistics (multivariate and univariate).
 * I taught highschool science and microbiology in college.

# Education


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

require(xfun)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )

xfun::pkg_attach2(packages, message = FALSE)

source(file = here::here("C:/Users/Owner/OneDrive - UQAM/Documents/vie/biostats/vitae/script_cv/","info.R"))
#"C:\Users\Owner\OneDrive - UQAM\Documents\vie\biostats\vitae\script_cv\info.R"
```

# Employment

```{r}

work %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
    where = where
  )

```

\pagebreak

# Education

```{r EDUCATION}

edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = where
  )

```

# Skills

```{r SKILLS}

skills %>%
  detailed_entries(
    with = area,
    what = skills
  )

```

# Honors

```{r HONORS}

honors %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

\pagebreak

# Projects

```{r PROJECTS}

projects %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Works

```{r WORKS}

works %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Certifications

```{r CERTIFICATIONS}

certifications %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

\pagebreak

<!-- ```{r} -->
<!-- library(tibble) -->
<!-- tribble( -->
<!--   ~ Degree, ~ Year, ~ Institution, ~ Where, -->
<!--   "Bachelors", "2018-21", "UQAM", "Montreal, Quebec", -->
<!--   "M. Sc in biological sciences", "expected end: January 2025", "UQAM", "Montreal, Quebec", -->
<!-- ) %>% -->
<!--   detailed_entries(Degree, Year, Institution, Where) -->
<!-- ``` -->

<!-- # Nobel Prizes -->

<!-- ```{r} -->
<!-- # tribble( -->
<!-- #   ~Year, ~Type, ~Desc, -->
<!-- #   1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel", -->
<!-- #   1911, "Chemistry", "Awarded for the discovery of radium and polonium" -->
<!-- # ) %>% -->
<!-- #   brief_entries( -->
<!-- #     glue::glue("Nobel Prize in {Type}"), -->
<!-- #     Year, -->
<!-- #     Desc -->
<!-- #   ) -->
<!-- ``` -->

<!-- # Publications -->

<!-- ```{r} -->
<!-- library(dplyr) -->
<!-- knitr::write_bib(c("vitae", "tibble"), "packages.bib") -->

<!-- bibliography_entries("packages.bib") %>% -->
<!--   arrange(desc(author$family), issued) -->
<!-- ``` -->
